### 2016-02-14 README.Rmd
updated README
few typo fixes

This package is the second iteration of my attempt at cloning the super cool and way sexier "csv-fingerprint" from flowing data - see [here](https://github.com/setosa/csv-fingerprint) and [here](https://flowingdata.com/2014/08/14/csv-fingerprint-spot-errors-in-your-data-at-a-glance/). Initially I had named the package "footprintr", to keep in spirit with the name "csv-fingerprint". However, after a little more thought and usage, I felt that "footprintr" didn't actually describe what was going on with the pacakge, and what it does, and so "visdat" was born.

# What does it do?

Initially inspired by `csv-fingerprint`, `vis_dat` helps you visualise a dataframe and "get a look at the data" by displaying the variable classes in a dataframe as a plot with `vis_dat`, and getting a brief look into missing data patterns `vis_miss`.

@@

>>>>

# What does visdat do?

Initially inspired by [`csv-fingerprint`](https://github.com/setosa/csv-fingerprint), `vis_dat` helps you visualise a dataframe and "get a look at the data" by displaying the variable classes in a dataframe as a plot with `vis_dat`, and getting a brief look into missing data patterns `vis_miss`.

@@

# Thank yous

Thank you to @jennbc, whose [tweet](https://twitter.com/JennyBryan/status/679011378414268416) got me thinking about this, and for her code contributions.

Thanks also to Noam Ross for his suggestions on using plotly with visdat.
